\documentclass[a4paper]{article}

\usepackage{fullpage} % Package to use full page
\usepackage{parskip} % Package to tweak paragraph skipping
\usepackage{tikz} % Package for drawing
\usepackage{amsmath}
\usepackage{hyperref}

\title{CSCI 39536-01 Intro to Robotics}
\author{Instructor: Jaime Canizales}
\date{Monday - Wednesday 4:00 - 5:15pm pm North Bldg C107, Spring 2023}

\begin{document}
\maketitle

\textbf{Textbooks:} Introduction To Robotics Mechanics And Control 3rd Edition. John J. Craig. ISBN: 9780201543612\\
Probablistic robotics sebastian thurn\\

\textbf{Email:} Jaime.Canizales@hunter.cuny.edu \\
\textbf{Office Hours:} By appointment.

\textbf{Course Description:}\\ 
\textbf{Part 1 Mathematics of Robotics}
The first part of the semester we will cover the necessary/fundamental topics in mathematics needed to have a deep understanding of robotics. Topics will include a review of linear algebra and probability theory, spatial descriptions and transformations(2D and 3D), manipulator kinematics, and algorithms relating to robot vision and navigation.

\textbf{Part 2 Robot Components and Programming}
The second part of the semester will be more hands on and project oriented. We will discuss different types of robot hardware, such as robot joints, cameras, lidars, odometer, kinect, and more. We will also learn the basics of programming in Robot Operating System (ROS), which is an open-source framework for controlling and communicating with robots.

\textbf{Grading: } \\
Midterm Exam: \hspace{11mm} 30\% \\
Final Exam: \hspace{17mm} 30\% \\
Assignments/Projects: \hspace{1mm} 40\% \\

\textbf{Assignments: } There will be four assignments/projects, which will be posted on blackboard.

\textbf{Hunter College Official Policies:}\\
Hunter College regards acts of academic dishonesty (e.g., plagiarism, cheating on examinations, obtaining
unfair advantage, and falsification of records and official documents) as serious offenses against the values of
intellectual honesty. The college is committed to enforcing the CUNY policy on Academic Integrity and will
pursue cases of academic dishonesty according to the Hunter College Academic Integrity Procedures.
\par In compliance with the American Disability Act of 1990 (ADA) and with Section 504 of the Rehabilitation
Act of 1973, Hunter College is committed to ensuring educational parity and accommodations for all students
with documented disabilities and/or medical conditions. It is recommended that all students with documented
disabilities (Emotional, Medical, Physical and/or Learning) consult the Office of AccessABILITY located in
Room E1124 to secure necessary academic accommodations. For further information and assistance please call
(212-772-4857)/TTY (212-650-3230)\\\\\\
\newpage
\end{document}